Catchy Part: Surveying Users' Perceptions of Threats for Wearable Devices

### 2014-12-20 wearables_survey.tex
Rough of survey section done.

\begin{abstract}
Hello world.
\end{abstract}

@@

\keywords{Privacy, User Studies, Ubiquitous Computing,Internet of Things} % NOT required for Proceedings

@@

@@

@@

Motivate the fact that this is important here! Mention ubiquitious computing, preventing security threats, etc.

\subsection{Calibrating with Existing Works}
(REDO) We used the same format as Adrienne's paper so that we can compare our results to the ones that she got in her study for mobile devices. Mobile devices threats are well studied and the closest well-researched thing to wearable device threats.

We used a prompt similar to Fischoff's study so that we could compare our results to the ones that he got in his study, and to put more of the new technologies onto the risk/benefit map. This way, we can have a sense of the risk and benefit with respect to well-studied and more familiar technologies.

\subsection{Validation}
(REDO) We conducted a focus group to look over the list, brainstorm more scenarios, and clarify any scenarios which were unclear (we also used this time to time the survey and make sure the formatting was clear.

>>>>

\begin{abstract}
(Okay, kind of intimidated with writing the abstract. My plan is to write intro/conclusion first and then condense it into here, while nodding off to the contributions that we made.) At the very least, I can say that we studied user perceptions for threats in wearable devices, along with user perceptions of risk and benefit for emerging technologies and what they thought was the biggest risk for using wearable devices. Data type, data recipient, and device type all matter different amounts. All new technologies were perceived to be low risk low benefit but we think this is because people are unfamiliar with these technologies. Privacy was the number one concern, followed by security, then health, money, social norms changing and social stigma. Fantastic ending sentence here.
\end{abstract}

@@

\keywords{Privacy, Security, User Studies, Risk Perception, Ubiquitous Computing, Wearables} % NOT required for Proceedings

@@

We need to investigate the threat landscape and people's privacy concerns now, before wearables are widely adopted, or designed without these considerations in mind. So although our research is at at time when things are rapidly changing and most people don't have wearables, it is crucial to do the research now so we can prevent badness later.

@@

We also study risk. Mention Fischoff here. This is a very seminal paper in risk perception and it also studies how safe enough something has to be before people can accept something. I will talk about how I model my work in the next section, Survey, just give it a nod here and go into it later. Also mention at least a couple more works related to risk perception here to round it off.

@@

We already motivated why ubiquitous computing is relevant and we need to do it, so no need to do it here. In the end, we ended up focusing questions on new capabilities that wearables have that smartphones and other devices do not, existing sensors, any concerns which might infringe on security and privacy, along with a couple investigative ones (like if someone recorded all your conversations but never shared it, are you going to be upset? that might be taken out of this paper, but still).

\subsection{Calibrating with Existing Works}
(REDO) Mobile devices threats are well studied and the closest well-researched thing to wearable device threats. We used the same format as Adrienne's paper so that we can compare our results to the ones that she got in her study for mobile devices. We purposed used the same scale and question format as she did in her study, but it's a pretty defensible scale to use anyway and the wording was about consistent with how we were going to do it anyway. Defend the likert scale use and the wording of the question a bit here. Because it is similar, and we also had calibrating questions, we can compare the threats with respect to existing threats studied. We're so relevant, yay.

We used a prompt similar to Fischoff's study so that we could compare our results to the ones that he got in his study, and to put more of the new technologies onto the risk/benefit map. This way, we can have a sense of the risk and benefit with respect to well-studied and more familiar technologies. This also makes the results that we have more accurate and tangible, since people have anchors to base their assessments off of, rather than comparing a bunch of things that seem nebulous to them.

\subsection{Validation}
(REDO) We conducted a focus group to look over the list, brainstorm more scenarios,  and get question feedback. We got a small sample of results (which were guided so we through them out, but it was helpful to know what we might expect) and clarify any scenarios which were unclear. Logistically, we also used this time to time the survey, made sure the survey worked, and other things. Quick demographics of the focus group here--(fix later) 12 people, X\% male, average age Y, with education ranging from A to B and professions including student, artist, business person, court judge, etc.
